### 2020-02-08 glossary.tex
Added Data Preprocess
Added test plan
Work load precipitation and water level
Work Load creation
Work Load - System Configuration
Update the summary

\newacronym{nwm}{NWMs}{Numerical Weather Models}
\newacronym{NetCDF}{NetCDF}{Network Common Data Form}
\newacronym{soa}{SOA}{Service Oriented Architecture}
\newacronym{wrf}{WRf}{Weather Research and Forecast}
\newacronym{esb}{ESB}{Enterprise Service Bus}
\newacronym{microservice}{Microservice}{Microservice Architectire}

>>>>

\newacronym{nwm}{NWMs}{Numerical Weather Models}
\newacronym{netCDF}{netCDF}{Network Common Data Form}
\newacronym{soa}{SOA}{Service Oriented Architecture}
\newacronym{wrf}{WRF}{Weather Research and Forecast}
\newacronym{esb}{ESB}{Enterprise Service Bus}
\newacronym{microservice}{Microservice}{Microservice Architecture}

\newacronym{mysql}{MySQL}{MySQL}
\newacronym{influxdb}{InfluxDB}{InfluxDB}
\newacronym{redis}{Redis}{Redis}
\newacronym{mongodb}{MongoDB}{MongoDB}
\newacronym{k8s}{K8s}{Kubernetes}
\newacronym{eks}{AWS EKS}{Amazon Elastic Kubernetes Service}

\newacronym{go}{Go Lang}{Go Programming Language}
\newacronym{rps}{RPS}{Requests Per Second}
\newacronym{api}{API}{Application Programming Interface}
\newacronym{jmeter}{JMeter}{Apache JMeter}
\newacronym{rps}{RPS}{Request per Second}

### 2020-02-08 results/sec_2-work_load.tex
Update Obs Full test 24 and 48 request size
Update the summary

TODO
\subsubsection{closed vs. open workload models} \cite{Haggett1998AnWales}
\begin{itemize}
    \item \emph{closed system model} a new request is only triggered by the completion of a previous request, following by a think time. System has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
    \item \emph{open system model} new requests arrival independently of completions, e.g. according to a stochastic process or fixed trace. System has no negative feedback.
\end{itemize}
While implementing the test cases for \acrshort{wdias}, it uses Concurrency Thread Group with Throughput Shaping Timer because of it support the open workload approach.
Using other thread groups, it required to find exact number of threads and timer delays that produce desired number of requests per second (RPS) to server. Which is known as the \emph{closed workload}.
With using Throughput Shaping Timer, it only need to configure the \acrfull{rps}. When combine this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target RPS \cite{Haggett1998AnWales} TODO.

@@

\subsection{System Configuration}
As described in the \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes. \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications. For the performance study uses \acrfull{eks}. There are many \acrshort{k8s} solutions available such as GCP, Azure, Digital Ocean etc on the cloud.

>>>>

TODO
\subsubsection{closed vs. open workload models} \cite{Haggett1998AnWales}
\label{subse:closed_vs_open_workload}
\begin{itemize}
    \item \emph{closed system model} a new request is only triggered by the completion of a previous request, following by a think time. System has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
    \item \emph{open system model} new requests arrival independently of completions, e.g. according to a stochastic process or fixed trace. System has no negative feedback.
\end{itemize}
While implementing the test cases for \acrshort{wdias}, it uses Concurrency Thread Group with Throughput Shaping Timer because of it support the open workload approach.
Using other thread groups, it required to find exact number of threads and timer delays that produce desired number of requests per second (RPS) to server. Which is known as the \emph{closed workload}.
With using Throughput Shaping Timer, it only need to configure the \acrfull{rps}. When combine this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target RPS \cite{Haggett1998AnWales} TODO.

@@

\subsection{System Configuration}
\label{sub:test_sys_config}
As described in the \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes. \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications. For the performance study uses \acrfull{eks}. There are many \acrshort{k8s} solutions available such as GCP, Azure, Digital Ocean etc on the cloud.

### 2020-02-08 summary/sec_1-summary.tex
Update the summary

As summary of the proposed system, it's performance and conclusion over the results.

>>>>

In order to enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}s. Most of existing weather data systems are proprietary or close sourced, or not up to date with the existing cloud computing technologies.
We proposed an extendable open source Weather Data Integration and Assimilation Systems which is known as \acrshort{wdias}. It focused on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data. And compatible with current cloud computing technologies and architecture patterns.

First the architecture starts with Service Oriented Architecture using a \acrfull{esb}, and then moved to Actor model based architecture. After comparing the disadvantages of using such architecture with the system requirements, final architecture come up with modern microservice architecture.
Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data. The system uses \acrshort{influxdb} timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netcdf} for storing Grid timeseries data.
Also the system provide a generic open mechanism to integrate new modules as extension in order to enhance the features of the system. This capability enable to integrate weather data preprocessing flows as extension modules.
The extension API provide easy access to create and modify the extension triggers on the fly without stopping the system or any downtime in order to change the configurations.
The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting geo based queries.

\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \ref{sub:test_sys_config}.
During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the work load. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the work load with the given configurations.

### 2020-02-08 summary/sec_2-future_work.tex
Update the summary

\paragraph{Add Alerting extension modules}
At the moment, extensions only support On Change and On Time events. But it will be good to have event trigger support based on reconfigured alert level.

\paragraph{Add Publisher Subscriber extension modules}
The \acrshort{wdias} better to be capable of triggering external systems based on the events such as webhooks.

>>>>

\paragraph{Alerting extension modules}
At the moment, extensions only support On Change and On Time events. But it will be good to have event trigger support based on reconfigured alert level.

\paragraph{Publisher Subscriber extension modules}
The \acrshort{wdias} better to be capable of triggering external systems based on the events such as web hooks.
